Twists of supersymmetric gauge theories

### 2019-10-28 paper.tex
edits

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm gauge}$ here. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields. 
Since we will not need the explicit form of the coupling in the untwisted theory, we do not give the formula here. 
Let $S_{\rm BV} = S_{\rm gauge} + S_{\rm matter} + S_{\rm couple}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

The BV action is clearly Poincar\'{e} invariant, so there is an interaction $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R +.
\end{align*}
where $Q_\pm \in S_{\pm}$. 
As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
\[
I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
\]

@@

Note that $I^{(1)}$ is linear in the supersymmetry algebra, and $I^{(2)}$ is quadratic.
Thus, the induced action on the $4$-dimensional $\mc N=1$ theory by the supersymmetry algebra $\mf A$ is an $L_\infty$ action.

@@

\brian{should I say something about why the term $\{S_{\rm matter}, I^{(1)}\} = 0$.}
The equality $\{S_{\rm matter}, I^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for concreteness. 
The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
\end{align*}
The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
\begin{align*}
\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+)) 
\end{align*}
\brian{Get the signs right and these terms should cancel.}

The BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$ reads:
\[
\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
\]
Now
\begin{align*} 
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
\end{align*}
In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative. 
Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
Thus, this calculation implies
\[
\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
\]
for all $Q_\pm, Q_\pm'$.

Next, we prove the following lemma involving the pieces of $I^{(1)}_{\rm matter}$, $I^{(2)}_{\rm matter}$ involving $\psi_\pm$.
This will finish the proof that the pure matter sector $\fS_{\rm matter}$ satisfies the classical master equation. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\} = 0.
\]
\end{lem}
\begin{proof}

\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = Fierz / 3 \psi \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

@@

There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
\begin{itemize}
\item The twisted theory is a shifted cotangent theory in the BV formalism. 
This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively.

\item The action functional is invariant with respect to the group $\mr U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
\end{itemize}

>>>>

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a pair of opposite chirality Lie algebra valued Weyl spinor fields $\lambda_\pm$:
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$):
\[
(\phi, \Bar{\phi}, \psi_\pm) \in 
\]
The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ minimally coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
The field content for the BRST fields in the gauge sector is:
\[
(c, A, \lambda_\pm) \in (\Omega^0(\RR^4) \oplus \Omega^1(\RR^4) \oplus \Omega^0(\RR^4) \otimes \Pi S_\pm) \otimes \fg .
\]

For the chiral multiplet, the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$:
\[
(\phi, \psi_+) \in \Omega^0(\RR^4) \otimes (R \oplus R \otimes \Pi S_+) \;\;\; , \;\;\; (\Bar{\phi}, \psi_-) \in \Omega^0(\RR^4) \otimes (R^* \oplus R^* \otimes \Pi S_-) .
\]
We have written down the full BV action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm BV, gauge}$.

The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ chiral multiplet is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_{\pm}) = \int \d^4 x \; \<\d \phi , * \d \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]
Here $\<-,-\>_R$ denotes the duality pairing between the representation $R$ and its dual $R^*$.

There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields, which we record here:
\begin{align*}
S_{\rm couple} & = \pm g \int \<\psi_+, [\lambda_+, \phi]\>_R \pm g \int \<\psi_-, [\lambda_-, \Bar{\phi}]\>_{R^*} \\
& \pm g \int [A, \phi] \wedge * \d_{A} \Bar{\phi} \pm g \int [A, \Bar{\phi}] \wedge * \d_A \phi \\
& \pm g^2 \int (\phi \Bar{\phi}) * (\phi \Bar{\phi}) 
\end{align*}
\brian{add terms involving antifields}

The action
\[
S_{\rm BV} = S_{BV}(\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) = S_{\rm BV, gauge}(A, \lambda_\pm, \; {\rm a.f's}) + S_{\rm matter}(\phi, \Bar{\phi}, \psi_\pm) + S_{\rm couple} (\phi, \Bar{\phi}, \psi_\pm , A, \lambda_\pm, \; {\rm a.f's}) 
\]
is the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

The full BV action $S_{\rm BV}$ is clearly Poincar\'{e} invariant, so there is a functional $I_{\rm Poin}$ encoding the action by the $4$-dimensional Poincar\'{e} algebra.

The action of supersymmetry on the $4$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I^{(1)}_{\rm matter} (Q_+ + Q_-) & = \int \<\phi^*, (Q_+, \psi_+)\>_R + \int \<\Bar{\phi}^*, (Q_-, \psi_-)\>_R + \int \<\psi^*_+, \rho(\d \phi) Q_- \>_R + \int \<\psi_-^*, \rho(\d \Bar{\phi}) Q_+\>_R \\
I^{(2)}_{\rm matter} (Q_+ \otimes Q_-) & = \int \<\psi^*_- , \rho(\Gamma(Q_+, Q_-)) \psi_+^*\>_R + \brian{write this differently?}.
\end{align*}
where $Q_\pm \in S_{\pm}$. 
As usual, we will use the notation $\delta_Q$ to denote the endomorphism on fields satisfying
\[
I^{(1)}_{\rm matter} = \int \<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, \delta_Q(\phi + \Bar{\phi} + \psi_+ + \psi_-) \> .
\]

@@

Notice that we have not introduced any auxiliary fields, which is at the cost of us formulating the action of superysmmetry as an $L_\infty$ action by the super Lie algebra of supertranslations.

@@

The equality $\{S_{\rm matter}, I_{\rm matter}^{(1)}\} = 0$ simply says that $S_{\rm matter}$ is invariant under the usual linear supersymmetric action.
The argument for this is completely standard, see for instance \brian{refs}, but we repeat it here for completeness. 
The BV bracket involving terms in $S_{\rm matter}$ depending on $\phi,\Bar{\phi}$ is:
\begin{align*}
\frac{1}{2} \left\{ \int \d \phi \wedge * \d \Bar{\phi} \; , \; I_{\rm matter}^{(1)} \right\} & = \int \d (\<Q_+, \psi_+\>) \wedge * \d \Bar{\phi} + \int \d \phi \wedge * \d (\<Q_-, \psi_-\>) \\
& = \pm \int (\Gamma(\sd \dd \psi_+, Q_+), \d \Bar{\phi}) \pm \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) .
\end{align*}
The BV bracket involving terms in $S_{\rm matter}$ depending on $\psi_\pm$ is:
\begin{align*}
\frac{1}{2} \left\{\int \<\psi_+ , \sd \dd \psi_-\> \; , \; I_{\rm matter}^{(1)} \right\} & = \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\psi_+, \sd \dd (\rho(\d \Bar{\phi}) Q_+)\> \\ & =  \int \<\rho(\d \phi) Q_-, \sd \dd \psi_-\> = \int \<\sd \dd \psi_+, (\rho(\d \Bar{\phi}) Q_+)\> \\ & = \int (\d \phi, \Gamma(\sd \dd \psi_-, Q_-)) + \int (\d \Bar{\phi}, \Gamma(\sd \dd \psi_+, Q_+)) 
\end{align*}
\brian{Get the signs right and these terms should cancel.}

The computation of the remaining terms in the matter sector are summarized in the following lemma. 
\begin{lem}
\[
\d_{CE} I_{\rm Poin} + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\} = 0.
\]
\end{lem}
\begin{proof}

First, we compute the BV bracket $\{I_{\rm matter}^{(1)}, I_{\rm matter}^{(1)}\}$:
\[
\{I^{(1)}_{\rm matter}, I^{(1)}_{\rm matter}\}(Q_+ + Q_-, Q_+' + Q_-') = 2 \int \left\<\phi^* + \Bar{\phi}^* + \psi^*_+ + \psi_-^*, [\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] \left(\phi + \Bar{\phi} + \psi_+ + \psi_-\right) \right\>  .
\]
We first focus on terms involving variations of $\phi, \Bar{\phi}$:
\begin{align*} 
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\phi + \Bar{\phi}) & = (\delta_{Q_+} + \delta_{Q_-}) \left(\<Q'_+, \psi_+\>_+ + \<Q'_-, \psi_-\>_-\right) - (\delta_{Q'_+} + \delta_{Q'_-}) \left(\<Q_+, \psi_+\>_+ + \<Q_-, \psi_-\>_-\right) \\ & = \<Q'_+, \rho(\d \phi) Q_-\>_+ + \<Q'_-, \rho(\d \Bar{\phi}) Q_+\>_- -  \<Q_+, \rho(\d \phi) Q'_-\>_+ - \<Q_-, \rho(\d \Bar{\phi}) Q'_+\>_- \\ & = (\d (\phi + \Bar{\phi}), \Gamma(Q_+ + Q_-, Q_+' + Q_-')) \\ & = L_{[Q_++Q_-, Q_+'+Q_-']} (\phi + \Bar{\phi}) %\\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\phi + \Bar{\phi})
\end{align*}
In the third line we have used the identity $(v, \Gamma(Q_1, Q_2)) = \<\rho(v) Q_1, Q_2\>$ where $Q_i \in S$, $v \in V$, $\<-,-\>$ is the spinor pairing, and $(-,-)$ is the inner product on $V$. 
The third line follows from the relation $(\d \phi, v) = L_v (\phi)$ where $L_v$ is the Lie derivative.

Let $I_{\rm Poin}(\phi,\Bar{\phi})$ be the piece of $I_{\rm Poin}$ depending on $\phi, \Bar{\phi}$ and their antifields.
The last line above is simply the Lie derivative with respect to the translation invariant vector field $[Q_++Q_-, Q_+'+Q_-']$ on the field $\phi + \Bar{\phi}$, which is precisely the symmetry encoded by $I_{\rm Poin}$.
Thus, this calculation implies
\[
\left(\d_{CE} I_{\rm Poin}(\phi, \Bar{\phi}) + \frac{1}{2} \left\{I_{\rm matter}^{(1)}(\phi, \Bar{\phi}), I_{\rm matter}^{(1)}(\phi, \Bar{\phi})\right\} \right) (Q_+ + Q_- , Q_+' + Q_-') = 0
\]
for all $Q_\pm, Q_\pm'$.

Next, we focus on the terms in the statement of the lemma involving the functionals which on the fields $\psi_{\pm}$: $I_{\rm Poin}(\psi_{\pm})$, $I^{(1)}_{\rm matter}(\psi_{\pm})$, and $I^{(2)}_{\rm matter}$. 
We must show
\[
\left(\d_{CE} I_{\rm Poin}(\psi_\pm) + \{S_{\rm matter}, I_{\rm matter}^{(2)}\} + \frac{1}{2} \{I_{\rm matter}^{(1)}(\psi_\pm), I_{\rm matter}^{(1)}(\psi_\pm)\}\right) (Q_+, Q_-, Q_+' + Q_-') = 0.
\]
for all $Q_\pm, Q_\pm'$.

We start by computing the variation of $\psi_+ + \psi_-$:
\begin{align*}
[\delta_{Q_+ + Q_-}, \delta_{Q_+' + Q_-'}] (\psi_+ + \psi_-) & = Fierz / 3 \psi \\ & = \delta_{[Q_+ + Q_-, Q_+' + Q_-']} (\psi_+ + \psi_-) \pm \rho(\Gamma(Q_++Q_-, Q_+' + Q_-')) \cdot \sd \dd (\psi_+ + \psi_-) .
\end{align*}
\end{proof}

@@

There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
\begin{itemize}
\item The twisted theory is a shifted cotangent theory in the BV formalism. 
This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
\item The action functional is invariant with respect to the group ${\rm U}(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
\item The action functional is translation invariant, this follows from the fact that the untwisted theory has a 
\end{itemize}
